Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex
Added a reference to nuprl.  Wrote a basic introduction.

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels on the types.
Although we did not complete the full proof because we ran out of time, we were
able to find small inaccuracies and subtleties in the proofs from the paper we
based our proof on.  We discuss what would be involved in completing the proof
and how this relates to other work.

@@

Introduce idea and outline what it will require us to do.  Explain where we're
starting from (Pottier and Simonet) at a high level.  Justify why this is an
interesting problem that needs tackling.

\section{\langName}

@@

\section{Proof of Noninterference}

@@

\section{Related Work}

@@

\section{Future Work}

@@

\section{Conclusion}

>>>>

In this paper we discuss our experience trying to mechanize a proof of
noninterference for a simple language with security labels, \langName.  Although
we did not complete the full noninterference proof because we ran out of time,
we were able to find small inaccuracies and subtleties in the proofs from the
paper we based our proof on.  We discuss what would be involved in completing
the proof and how this relates to other work.

@@

Verified systems have been growing in popularity recently with the rise of proof
assistants like Coq and NuPRL~\cite{coqart,nuprl}.  These systems allow a
programmer to write programs and have proofs, which are checked and compiled by
the system, which can assert various properties about the programs.  As we will
discuss in Section~\ref{sec:related}, these systems have been used to formalize,
prove correct, and implement systems that have verified properties.  This allows
for programmers to be more confident in their languages and programs, ensuring
that the properties they want are actually properties of their work.

Interestingly, as far as we know there has not been work to formalize and verify
a language, like Jif~\cite{myers1999jflow} or FlowCaml~\cite{simonet2003flow},
that has a type system for enforcing information flow security policies.  For
languages like these and other systems related to security, it is desirable for
the program to be accompanied with a proof of the security properties it
enforces.  Our goal is to make progress towards verifying the correctness of a
compiler for a language with information flow types that programmers will want
to use.

A verified compiler for a language like Jif would require a proof of
noninterference, which asserts that any program in the language will never
produce different outputs for low security items if only the high security input
values are varied.  Thus, in this paper we discuss our experience working
towards proving this theorem for a simple information flow type system as a
first step towards creating a verified information flow compiler.

Our language, \langName,  and proof are a simplified version of what is
presented in Simonet and Pottier's work on information flow for an ML-like
language, \origLang~\cite{InfoFlowML}.  This proof proceeds by designing a
language that includes values which represent two different alternatives,
representing the different values of high security items in two different
executions of the program.  The proof then becomes a matter of proving that if
the program is typed with a low security label, this does not produce a value
that could be different between two different executions of the program.

In this paper we will present our simplified language, \langName,
along with the semantics and type system (Section~\ref{sec:lang}).  We will then
present a natural language, human readable, proof of noninterference for the
language and discuss our experiences with mechanizing this proof in the Coq
proof assistant (Sections~\ref{sec:proof} and \ref{sec:mechanizing}).  Finally,
we will discuss related work, next steps, and conclude
(Sections~\ref{sec:related}, \ref{sec:future}, and \ref{sec:conclusion}).

\section{\langName}
\label{sec:lang}

@@

\section{Proof of Noninterference}
\label{sec:proof}

@@

\section{Related Work}
\label{sec:related}

@@

\section{Future Work}
\label{sec:future}

@@

\section{Conclusion}
\label{sec:conclusion}
